Implications of afforestation policies for global markets

### 2023-05-31 paper.Rmd
Update paper.Rmd

The global gains that can be realized from afforestion, however, are uncertain, with estimates ranging from 42 gigatonnes [@veldman2019] to 205 gigatonnes [@bastin2019], as afforestation appears to not provide the same benefits in all regions of the world. In particular, boreal forests appear to provide the smallest net benefits, as the carbon sequestrations benefits of conifer forests are mitigated by the reduction in albedo in winter [@mykleby2017] [@li2015]. Moreover, coniferous forests have been shown to increase soil organic carbon less than broadleaf forests [@guo2021]. With tropical forests, a strong positive result is derived from afforestation, as the carbon sequestration benefit is complemented by a cooling impact due to changes in both albedo and evapotranspiration, and with temperate forests, the impact of afforestation is also shown to be positive, albeit less strongly so due to a winter warming effect [@li2015].

@@

[@Humpenöder2014].

>>>>

The global gains that can be realized from afforestion, however, are uncertain, with broad estimates of cumulative sequestration ranging from 42 gigatonnes to 700 gigatonnes by the end of the century [@veldman2019]  [@bastin201]  [@Humpenöder2014]. In addition, the amount of land conversion that would be required also varies greatly, with estimates ranging from 0.3 billion hectares to 2.8 billion hectares [@veldman2019]  [@bastin201]  [@Humpenöder2014].  In many cases, these results suggest massive losses in pasture and cropland.

Moreover, afforestation appears to not provide the same benefits in all regions of the world. In particular, boreal forests appear to provide the smallest net benefits, as the carbon sequestrations benefits of conifer forests are mitigated by the reduction in albedo in winter [@mykleby2017] [@li2015]. Moreover, coniferous forests have been shown to increase soil organic carbon less than broadleaf forests [@guo2021]. With tropical forests, a strong positive result is derived from afforestation, as the carbon sequestration benefit is complemented by a cooling impact due to changes in both albedo and evapotranspiration, and with temperate forests, the impact of afforestation is also shown to be positive, albeit less strongly so due to a winter warming effect [@li2015].

@@

.
